FastSRM: A fast, memory efficient and identifiable implementation of the shared response model

### 2021-11-29 paper/main.tex
update setup and paper

We have the following result:
\begin{proposition}[Optimal atlas for probabilistic FastSRM]
  Let $(A_i)_i, \sigma_i, \Sigma_s$ be the solution obtained by probabilistic SRM on data
  $\xb_i$ and $(A_i')_i, \sigma_i', \Sigma_s'$ the solution obtained by ProbSRM on
  data $\zb_i = U_{\xb_i}^{\top} \xb_i$ but where updates:
  \begin{align}
    \sigma_i^2 \leftarrow \frac1{k} (\EE[\| \zb_i - A_i \EE[\sbb|\zb]\|^2] + \| \diag(\VV[\sbb | \zb]) \|^2)
  \end{align}
  are replaced by updates
  \begin{align}
    \sigma_i^2 \leftarrow \frac1{v} (\EE[\| \zb_i - A_i \EE[\sbb|\zb]\|^2] + \| \diag(\VV[\sbb | \zb]) \|^2)
  \end{align}
  .
  %
  Then $A_i = U_{\xb_i}A_i'$, $\sigma_i =
  \sigma_i'$ and $\Sigma_s = \Sigma_s'$.
  %

@@

While brainiak and nilearn are useful to reproduce some of our experiments, they
are not strong dependencies and FastSRM only needs numpy ($\geq 1.12$), scipy
($\geq 0.18.0$), matplotlib ($\geq 2.0.0$), scikit-learn ($geq 0.23$), pytest
($\geq 6.2.5$) , joblib ($\geq 1.1.0).

>>>>

We have the following result:
\begin{proposition}[Optimal atlas for probabilistic FastSRM]
  Let $(A_i)_i, \sigma_i, \Sigma_s$ be the solution obtained by probabilistic SRM on data
  $\xb_i$ and $(A_i')_i, \sigma_i', \Sigma_s'$ the solution obtained by ProbSRM on
  data $\zb_i = U_{\xb_i}^{\top} \xb_i$ but where updates:
  \begin{align}
    \sigma_i^2 \leftarrow \frac1{t} (\EE[\| \zb_i - A_i \EE[\sbb|\zb]\|^2] + \| \diag(\VV[\sbb | \zb]) \|^2)
  \end{align}
  are replaced by updates
  \begin{align}
    \sigma_i^2 \leftarrow \frac1{v} (\EE[\| \zb_i - A_i \EE[\sbb|\zb]\|^2] + \| \diag(\VV[\sbb | \zb]) \|^2)
  \end{align}
  .
  %
  Then $A_i = U_{\xb_i}A_i'$, $\sigma_i =
  \sigma_i'$ and $\Sigma_s = \Sigma_s'$.
  %

@@

While brainiak and nilearn are useful to reproduce some of our experiments, they
are not strong dependencies and FastSRM only needs numpy ($\geq 1.12$), scipy
($\geq 0.18.0$), matplotlib ($\geq 2.0.0$), scikit-learn ($\geq 0.23$), pytest
($\geq 6.2.5$) , joblib ($\geq 1.1.0$).
